Mixed effect tweedie model in TMB

### 2019-04-19 analysis/tmb-sensor-explore/2-fit-temperature.Rmd
move rds files to data folder

Load data
```{r}
# d_trawl1 <- readRDS(here::here("analysis/tmb-sensor-explore/sensor-data-processed.rds"))
# nrow(d_trawl1)
d_trawl <- readRDS(here::here("analysis/tmb-sensor-explore/dat-sensor-trawl-SST.rds"))
nrow(d_trawl)
# d_trawl$log_temperature_c <- log(d_trawl$temperature_c)
unique(d_trawl$year)
d_trawl[is.na(d_trawl$year), ]$year <- 2003
d_trawl <- d_trawl[!is.na(d_trawl$depth_m), ]
d_trawl <- d_trawl[!is.na(d_trawl$temperature_c), ]
d_trawl <- d_trawl[!is.na(d_trawl$SST), ]
d_trawl <- mutate(d_trawl,
  depth_scaled = arm::rescale(log(depth_m)),
  SST_scaled = arm::rescale(SST),
  depth_scaled2 = depth_scaled^2,
  depth_scaled3 = depth_scaled^3,
  shallow = ifelse(depth_m>50,0,1)
)
glimpse(d_trawl)
```

>>>>

Load data
```{r}
# d_trawl1 <- readRDS(here::here("analysis/tmb-sensor-explore/data/sensor-data-processed.rds"))
# nrow(d_trawl1)
d_trawl <- readRDS(here::here("analysis/tmb-sensor-explore/data/dat-sensor-trawl-SST.rds"))
nrow(d_trawl)
# d_trawl$log_temperature_c <- log(d_trawl$temperature_c)
unique(d_trawl$year)
d_trawl[is.na(d_trawl$year), ]$year <- 2003
d_trawl <- d_trawl[!is.na(d_trawl$depth_m), ]
d_trawl <- d_trawl[!is.na(d_trawl$temperature_c), ]
d_trawl <- d_trawl[!is.na(d_trawl$SST), ]
d_trawl <- mutate(d_trawl,
  depth_scaled = arm::rescale(log(depth_m)),
  SST_scaled = arm::rescale(SST),
  depth_scaled2 = depth_scaled^2,
  depth_scaled3 = depth_scaled^3,
  shallow = ifelse(depth_m>50,0,1)
)
glimpse(d_trawl)
```
